---
title: "Learn R Part I In-class Solutions"
format: html
editor: visual
---

Welcome to your first Quarto document! This is where you will try out all of the hands-on exercises in the workshop.

```{r}
# load packages
library(tidyverse)
```

## 05. How do I write and run code in a coding notebook?

Write and run code that finds the square root of 60

Hint: the square root function in R is `sqrt()`

```{r}
# find sq root
sqrt(60)
```

## 06. What is an object and how do I create one?

Create an object called `my_age` that stores your age, then call the object so it prints to the Console.

```{r}
# store age
my_age <- 32

# call age
my_age
```

## 08. How do I import data?

Load the David Bowie data using `read_csv()`. You can name your data frame object `bowie`

```{r}
# import data
bowie <- read_csv("data/david_bowie_spotify.csv")
```

## 09. How can I get to know my variables?

Using `summary()`, determine whether the mean or median of `energy` is greater.

```{r}
# look at danceability
summary(bowie$energy)
```

The median is larger than the mean (.71 vs. .66)

## 10. What are some ways I can transform my data?

### 10.1 Subset rows with `filter()`

Filter `bowie` to only contain songs that are on the "Low" album

```{r}
# keep Low album only
bowie |> 
  filter(album == "Low")
```

### 10.2 Subset columns with `select()`

Limit the columns in `bowie` to only include `track` and `speechiness`

```{r}
# limit columns
bowie |> 
  select(track, speechiness)
```

### 10.3 Sort rows with `arrange()`

Find the 3 most popular David Bowie songs (according to Spotify)

*Hint:* Browse the environment pane for the variable that measures this (it's at the bottom)

```{r}
# most popular songs
bowie |> 
  arrange(-popularity) |> 
  select(track, popularity)
```

"Starman", "Heroes", and "Rebel Rebel"

### 10.4 Create new variables with `mutate()`

Create a new variable in `bowie` that multiplies `danceability` by 100 (you pick the name of the new variable), then limit your columns to `track`, `danceability`, and your new variable.

Note: The symbol for multiplication in R is `*`

```{r}
# create new variable
bowie |> 
  mutate(dance100 = danceability * 100) |> 
  select(track, danceability, dance100)
```
