---
title: "Learn R Part I In-class Exercises"
format: html
editor: visual
---

Welcome to your first Quarto document! This is where you will try out all of the hands-on exercises in the workshop.

## 05. How do I write and run code in a coding notebook?

Write and run code that finds the square root of 60

Hint: the square root function in R is `sqrt()`

```{r}

```

## 06. What is an object and how do I create one?

Create an object called `my_age` that stores your age, then call the object so it prints to the Console.

```{r}

```

## 08. How do I import data?

Load the David Bowie data using `read_csv()`. You can name your data frame object `bowie`

```{r}

```

## 09. How can I get to know my variables?

Using `summary()`, determine whether the mean or median of `energy` is greater.

```{r}

```

## 10. What are some ways I can transform my data?

### 10.1 Subset rows with `filter()`

Filter `bowie` to only contain songs that are on the "Low" album

```{r}

```

### 10.2 Subset columns with `select()`

Limit the columns in `bowie` to only include `track` and `speechiness`

```{r}

```

### 10.3 Sort rows with `arrange()`

Find the 3 most popular David Bowie songs (according to Spotify)

*Hint:* Browse the environment pane for the variable that measures this (it's at the bottom)

```{r}

```

### 10.4 Create new variables with `mutate()`

Create a new variable in `bowie` that multiplies `danceability` by 100 (you pick the name of the new variable), then limit your columns to `track`, `danceability`, and your new variable.

Note: The symbol for multiplication in R is `*`

```{r}

```
